Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-23 paper/v2/paper-edited.tex
update with copyright information
fix heading capitalization and spelling mistakes

\setcopyright{acmcopyright}
\conferenceinfo{SIGCOMM '16}{August 22--26, 2016, Florianopolis, Brazil}

@@

\para{Problem Formulation}

@@

\para{Regret-free Preferences}
To order PGIR shadows ($\leq_{lp}$) for each router in a way that is policy-compliant under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}. A router (location) $l$ has a regret-free preference for a set of advertisements $A$ over $B$ if, whenever $l$ selects an advertisement to destination $d$ from $A$ over another from $B$, there is always some policy-compliant path to $d$ that is at least as good ($\leq_{rank}$ for the final node along the path) as any possible path (not necessarily from $l$) to $d$ if $l$ had selected an advertisement from $B$ instead. In other words, the preference of $A$ over $B$ at $l$ is regret-free if $l$ is never (under any failure) worse-off by choosing an advertisement from $A$ when available. The notion of regret-free preferences can be lifted to PGIR nodes by considering the set of advertisements available to each node.

@@

\para{A Preference Inference Algorithm}

@@

\para{Avoiding Loops}

@@

For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the PGIR for \CD{PG1}. Since we know aggregation will occur at $X$, and that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first and woul then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is now disconnected from $X$, 2 is a lower bound on the number of failures required to introduce an aggregation black hole for prefix \CD{PG1}. This process is repeated for other aggregation locations (\EG, $Y$).

@@

\para{Acknowledgements}
We thank R. Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper. This work is supported in part by the National Science Foundation awards CNS-1161595 and CNS-1111520 as well as a gift from Cisco.

>>>>

\CopyrightYear{2016} 
\setcopyright{acmcopyright}
\conferenceinfo{SIGCOMM '16,}{August 22-26, 2016, Florianopolis , Brazil}
\isbn{978-1-4503-4193-6/16/08}\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/2934872.2934909}

@@

\para{Problem formulation}

@@

\para{Regret-free preferences}
To order PGIR shadows ($\leq_{lp}$) for each router in a way that is policy-compliant under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}. A router (location) $l$ has a regret-free preference for a set of advertisements $A$ over $B$ if, whenever $l$ selects an advertisement to destination $d$ from $A$ over another from $B$, there is always some policy-compliant path to $d$ that is at least as good ($\leq_{rank}$ for the final node along the path) as any possible path (not necessarily from $l$) to $d$ if $l$ had selected an advertisement from $B$ instead. In other words, the preference of $A$ over $B$ at $l$ is regret-free if $l$ is never (under any failure) worse-off by choosing an advertisement from $A$ when available. The notion of regret-free preferences can be lifted to PGIR nodes by considering the set of advertisements available to each node.

@@

\para{A preference inference algorithm}

@@

\para{Avoiding loops}

@@

For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the PGIR for \CD{PG1}. Since we know aggregation will occur at $X$, and that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first and would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is now disconnected from $X$, 2 is a lower bound on the number of failures required to introduce an aggregation black hole for prefix \CD{PG1}. This process is repeated for other aggregation locations (\EG, $Y$).

@@

\para{Acknowledgments}
We thank R. Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper. This work is supported in part by the National Science Foundation awards CNS-1161595 and CNS-1111520 as well as a gift from Cisco.
